---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** 
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  134780 - C - Trevor Okinda                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  132840 - C - Sheila Wangui                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  131749 - C - Teresia Nungari                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  135203 - C - Tom Arnold                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   |                                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Lakers                                                                                                       
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## klaR ----
if (require("klaR")) {
  require("klaR")
} else {
  install.packages("klaR", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## e1071 ----
if (require("e1071")) {
  require("e1071")
} else {
  install.packages("e1071", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## readr ----
if (require("readr")) {
  require("readr")
} else {
  install.packages("readr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## LiblineaR ----
if (require("LiblineaR")) {
  require("LiblineaR")
} else {
  install.packages("LiblineaR", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## naivebayes ----
if (require("naivebayes")) {
  require("naivebayes")
} else {
  install.packages("naivebayes", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Load dataset

Load the PimaIndiansDiabetes dataset and check its structure

```{r Load dataset}
library(mlbench)
data("PimaIndiansDiabetes")
# Check the structure of the dataset
str(PimaIndiansDiabetes)
```

## Scale Data Transform


```{r Scale Data Transform}
# BEFORE
summary(student_performance_dataset)

model_of_the_transform <- preProcess(student_performance_dataset, method = c("scale"))
print(model_of_the_transform)
student_perfomance_dataset_scale_transform <- predict(model_of_the_transform,
                                          student_performance_dataset)
# AFTER
summary(student_perfomance_dataset_scale_transform)

```

Next, Center Data Transform

```{r Center Data Transform}
# BEFORE
summary(student_performance_dataset)

model_of_the_transform <- preProcess(student_performance_dataset, method = c("center"))
print(model_of_the_transform)
student_performance_dataset_center_transform <- predict(model_of_the_transform, # nolint
                                           student_performance_dataset)

# AFTER
summary(student_performance_dataset_center_transform)

```

# Standardize Data Transform


```{r Standardize Data Transform}
# BEFORE
summary(student_performance_dataset)


model_of_the_transform <- preProcess(student_performance_dataset,
                                     method = c("scale", "center"))
print(model_of_the_transform)
student_performance_dataset_standardize_transform <- predict(model_of_the_transform, # nolint
                                                student_performance_dataset)
# AFTER
summary(student_performance_dataset_standardize_transform)

```

## Normalize Data Transform

```{r Normalize Data Transform}
#### The Normalize Transform on the Student Performance Dataset ----
summary(student_performance_dataset)
model_of_the_transform <- preProcess(student_performance_dataset, method = c("range"))
print(model_of_the_transform)
student_performance_dataset_normalize_transform <- predict(model_of_the_transform, # nolint
                                              student_performance_dataset)
summary(student_performance_dataset_normalize_transform)

```

## Box-Cox Power Transform

```{r Box-Cox Power Transform}
summary(student_performance_dataset)


model_of_the_transform <- preProcess(student_performance_dataset, method = c("BoxCox"))
print(model_of_the_transform)
student_performance_dataset_box_cox_transform <- predict(model_of_the_transform, # nolint
                                                         student_performance_dataset)

# AFTER
summary(student_performance_dataset_box_cox_transform)

```

**etc.** as per the lab submission requirements. Be neat and communicate in a clear and logical manner.